Incentivizing Optimal Forecasting Groups in Prediction Markets

### 2017-04-26 optimal_forecasts/Final Paper/article_2.tex
Final writing of results

Here, the incentive scheme adapts to ensure that the market doesn't simply stop when the current proportions for the participating pool are very close or equal to the optimal proportions. One can see from the second subplot that the incentives for type $a$ and type $b$ oscillate as more individuals are incorporated into the pool.\\

Another interesting thing to note about the two subplots is how they change when the participating group size gets to be around 180. We see a large spike in the incentive for a type $b$ to participate as well as the proportion of the group that is of type $a$ to increase with respect to the optimal proportion. At this point, the available type $b$ agents have all participated.\\

@@

%------------------------------------------------
\section{Results}

\section{Discussion}

\subsection{Subsection One}

A statement requiring citation \cite{Figueredo:2009dg}.
\blindtext % Dummy text

\subsection{Subsection Two}

\blindtext % Dummy text

\begin{table}
\caption{Example table}
\centering
\begin{tabular}{llr}
\toprule
\multicolumn{2}{c}{Name} \\
\cmidrule(r){1-2}
First name & Last Name & Grade \\
\midrule
John & Doe & $7.5$ \\
Richard & Miles & $2$ \\
\bottomrule
\end{tabular}
\end{table}

@@

\bibitem [1]{1}
J. Wolfers and E. Zitzewitz. Prediction markets. \textit{The Journal of Economic Perspectives},
18(2):107-126, 2004.
\bibitem [2]{2}
 Joyce Berg, Robert Forsythe, Forrest Nelson, and Thomas Rietz. \textit{Results from
a Dozen Years of Election Futures Markets Research}, volume 1 of \textit{Handbook of
Experimental Economics Results}, chapter 80, pages 742-751. Elsevier, 2008.
\bibitem [3]{3}
P. J. Lamberson, Scott E. Page, (2012) \textit{Optimal Forecasting Groups}. \textit{Management Science} 58(4):805-810
\bibitem [4]{4}
Tilmann Gneiting and Adrian E. Raftery. Strictly proper scoring rules, prediction,
and estimation. \textit{Journal of the American Statistical Association}, 102(477):359-378,
March 2007.

>>>>

Here, the incentive scheme adapts to ensure that the market doesn't simply stop when the current proportions for the participating pool are very close or equal to the optimal proportions. One can see from the second subplot that the incentives for type $a$ and type $b$ oscillate as more individuals are incorporated into the pool.

Another interesting thing to note about the two subplots is how they change when the participating group size gets to be around 180. We see a large spike in the incentive for a type $b$ to participate as well as the proportion of the group that is of type $a$ to increase with respect to the optimal proportion. At this point, the available type $b$ agents have all participated.

@@

\subsubsection{Comparison to a Market Scoring Rule}

Originally, one goal was to compare the scheme proposed in this paper with the well-known market scoring rule \cite{5} in order to compare the accuracy of one to another in determining the aggregate prediction for the likelihood of an event happening. However, there are some structural differences between the two setups that makes making a fair comparison difficult. Most notably,

\section{Discussion and Future Work}

@@

\bibitem [1]{1}
J. Wolfers and E. Zitzewitz. Prediction markets. \textit{The Journal of Economic Perspectives},
18(2):107-126, 2004.
\bibitem [2]{2}
 Joyce Berg, Robert Forsythe, Forrest Nelson, and Thomas Rietz. \textit{Results from
a Dozen Years of Election Futures Markets Research}, volume 1 of \textit{Handbook of
Experimental Economics Results}, chapter 80, pages 742-751. Elsevier, 2008.
\bibitem [3]{3}
P. J. Lamberson, Scott E. Page, (2012) \textit{Optimal Forecasting Groups}. \textit{Management Science} 58(4):805-810
\bibitem [4]{4}
Tilmann Gneiting and Adrian E. Raftery. Strictly proper scoring rules, prediction,
and estimation. \textit{Journal of the American Statistical Association}, 102(477):359-378,
March 2007.
\bibitem [5]{5}
Hanson, Robin. \textit{Combinatorial information market design.} \textit{Information Systems Frontiers} 5.1 (2003): 107-119.
